Untitled

### 2022-12-14 draft_report.Rmd
12/14 updates

HaploQA is a web application developed by Kieth Sheppard for The Reinholdt's Lab in 2015 for the purpose of storing, increasing accessibility and quality controlling of micro array mice genotyping data. According to the HaploQA about website, 'On the import of a sample, the haplotype probabilities that are represented in the plots are calculated.' and the haplotype reconstruction process for the contributing founder strains is then done based on the calculated probabilities. The source codes of HaploQA was written in Python 3.

@@

Some crosses, such as DO and CC, have the same contributing founders across all individuals. The haplotype reconstructions can therefore be conducted for all individuals in the entire cross at the same time. The pipeline 'haplotype_reconstruction_pipeline' can be used for crosses with consistent contributing founders for such purpose. Whereas the mutant crosses, such as MiniMUGA, contains individuals with mutate mice where all individuals may have different contributing founder strains. Haplotype reconstructions for these types of crosses need to conducted individually for each sample, and therefore, the pipeline 'sample_haplotype_reconstruction' should be used.

@@

```{r}
do_results <- haplotype_reconstruction_pipeline('DO', list_pheno, qtl2_file_gen = F, samples_gen = F)

@@

```{r}
cc_results <- haplotype_reconstruction_pipeline('CC', list_pheno, qtl2_file_gen = F, samples_gen = F, truth_model = F)

>>>>

HaploQA is a web application developed by Kieth Sheppard for The Reinholdt's Lab in 2015 for the purpose of storing, increasing accessibility and quality controlling of micro array mice genotyping data. According to the HaploQA about website, 'On the import of a sample, the haplotype probabilities that are represented in the plots are calculated.' and the haplotype reconstruction process for the contributing founder strains is then done based on the calculated probabilities. The source codes of HaploQA was written in Python 3 and JavaScript.

@@

Some crosses, such as DO and CC, have the same contributing founders across all individuals. The haplotype reconstructions can therefore be conducted for all individuals in the entire cross at the same time, and the pipeline 'haplotype_reconstruction_pipeline' can be used for crosses with consistent contributing founders for such purpose. Whereas the mutant crosses, such as MiniMUGA, contains individuals with mutate mice where all individuals may have different contributing founder strains. Haplotype reconstructions for these types of crosses need to conducted individually for each sample, and therefore, the pipeline 'sample_haplotype_reconstruction' should be used.

@@

```{r message=FALSE}
do_results <- haplotype_reconstruction_pipeline('DO', list_pheno, qtl2_file_gen = F, samples_gen = F)

@@

```{r}
cc_results <- haplotype_reconstruction_pipeline('CC', list_pheno, qtl2_file_gen = F, samples_gen = F)
